### 2014-12-05 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor fixes based on reviewer comments

\begin{tabbing}
\hspace{1.5in} \= \\
BC \> Battalion Chief \\
E \> Engine \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
IC \> Incident Command \\
LODD \> Line of Duty Death \\
NIOSH \> National Institute for Occupational Safety and Health \\
NIST \> National Institute of Standards and Technology \\
SFPE \> Society of Fire Protection Engineers \\
\end{tabbing}

@@

The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located at and above street level, and two stories were located below street level. The first floor and second floor (i.e., the two stories at and above street level) each had an interior floor area of 136~m$^2$ (1,470~ft$^2$). The interior walls were composed of gypsum board over insulated wood framing. The entrance stairs located on the front side of the structure led to the front door and an interior landing, which allowed access to the first floor (ten~stairs down) or the second floor (five~stairs up).

>>>>

\begin{tabbing}
\hspace{1.5in} \= \\
BC \> Battalion Chief \\
E \> Engine \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
IC \> Incident Command \\
LODD \> Line of Duty Death \\
LODI \> Line of Duty Injury \\
NIOSH \> National Institute for Occupational Safety and Health \\
NIST \> National Institute of Standards and Technology \\
SFPE \> Society of Fire Protection Engineers \\
UL \> Underwriters Laboratories
\end{tabbing}

@@

The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located at and above street level, and two stories were located below street level. The first floor and second floor (i.e., the two stories at and above street level) each had an interior floor area of 136~m$^2$ (1470~ft$^2$). The interior walls were composed of gypsum board over insulated wood framing. The entrance stairs located on the front side of the structure led to the front door and an interior landing, which allowed access to the first floor (ten~stairs down) or the second floor (five~stairs up).
